---
title: "simpleRegress"
author: "April Galvan"
output: 
  html_document:
    number_sections: true
    toc: true
    toc_depth: 5
date: "`r Sys.Date()`"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## make a simple regression model

```{r}
bears <- read.csv(file="BEARS.csv",header = TRUE)
```

## Model LENGTH ~ NECK  this is an example  

#NECK

```{r}
simp <- lm(LENGTH~NECK,data=bears)
plot(LENGTH~NECK,data=bears)
abline(simp)
summary.lm(simp)
```

## now predict the length of a bear who has a neck of 17, 22 and 26

```{r}
new <- data.frame(NECK=c(17,22,26))
predict(simp,new)
predict(simp,new,se.fit=TRUE)
```
## Surely there is another variable that can better predict LENGTH than NECK. Find one and compare its performance to that of neck by it value of Adjusted-Rsquared (bigger is better).


# WEIGHT

```{r}
simp <- lm(LENGTH~WEIGHT,data=bears)
plot(LENGTH~WEIGHT,data=bears)
abline(simp)
summary.lm(simp)
```

# HEADLEN

```{r}
simp <- lm(LENGTH~HEADLEN,data=bears)
plot(LENGTH~HEADLEN,data=bears)
abline(simp)
summary.lm(simp)
```

# CHEST

```{r}
simp <- lm(LENGTH~CHEST,data=bears)
plot(LENGTH~CHEST,data=bears)
abline(simp)
summary.lm(simp)
```

# SEX

```{r}
simp <- lm(LENGTH~SEX,data=bears)
plot(LENGTH~SEX,data=bears)
abline(simp)
summary.lm(simp)
```

# AGE

```{r}
simp <- lm(LENGTH~AGE,data=bears)
plot(LENGTH~AGE,data=bears)
abline(simp)
summary.lm(simp)
```

# HEADWTH

```{r}
simp <- lm(LENGTH~HEADWTH,data=bears)
plot(LENGTH~HEADWTH,data=bears)
abline(simp)
summary.lm(simp)
```

# NECK SQUARED

```{r}
simp <- lm(LENGTH~I(NECK**2)+NECK,data=bears)
plot(LENGTH~I(NECK**2)+NECK,data=bears)
abline(simp)
summary.lm(simp)
```

# The best variable 

The best variable to compare LENGTH was HEADLEN. This is because it gave the greater value for the adjusted R-squared, which was 0.843. After we looked at the model of LENGTH~NECK and compared the orignal model to the new NECK SQUARED model, which did not really change the value of the adjusted R-squared.